---
title: "Lab 07 - Conveying the right message through visualisation"
author: "Colin Li"
date: "3/1/2023"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(haven)
library(ggplot2)
library(ggsci)
library(plotly)
```


this graph is very strange, I don't understand why there are two y axes and why they correspond to different values. Shouldn't the colors be legends? The lines are also confusing: the background lines do not match the dates. For example, for masked counties on 07/13/2020, I don't know whether the cases are 20 or 22. Essentially, I think the graph is trying to say that mask mandate counties have lower cases overtime. 


### Exercise 1
```{r}
mask <- tribble(
  ~date, ~count,
  "07/12/2020", 26,
  "07/13/2020", 20,
  "07/14/2020", 20,
  "07/15/2020", 20.5,
  "07/16/2020", 20,
  "07/17/2020", 20,
  "07/18/2020", 20.5,
  "07/19/2020", 20,
  "07/20/2020", 20.5,
  "07/21/2020", 21.5,
  "07/22/2020", 20,
  "07/23/2020", 20, 
  "07/24/2020", 20.5,
  "07/25/2020", 19,
  "07/26/2020", 20,
  "07/27/2020", 17,
  "07/28/2020", 16.2,
  "07/29/2020", 16.3,
  "07/30/2020", 16.4,
  "07/31/2020", 16.1,
  "08/01/2020", 16.2,
  "08/02/2020", 16,
  "08/03/2020", 16.1,
)

nomask <- tribble(
  ~date, ~count,
  "07/12/2020", 9.9,
  "07/13/2020", 9.1,
  "07/14/2020", 9.3,
  "07/15/2020", 9.9,
  "07/16/2020", 9.9,
  "07/17/2020", 9.7,
  "07/18/2020", 9.7,
  "07/19/2020", 9,
  "07/20/2020", 8.5,
  "07/21/2020", 8.5,
  "07/22/2020", 8.6,
  "07/23/2020", 8.5, 
  "07/24/2020", 9.9,
  "07/25/2020", 9.9,
  "07/26/2020", 10.1,
  "07/27/2020", 9.7,
  "07/28/2020", 9.7,
  "07/29/2020", 9.75,
  "07/30/2020", 10,
  "07/31/2020", 9,
  "08/01/2020", 9.1,
  "08/02/2020", 9,
  "08/03/2020", 9.2,
)

merged_data <- merge(mask, nomask, by = "date")

merged_data$mask <- merged_data$count.x
merged_data$nomask <- merged_data$count.y


#I want to create a condition variable and combine cases into one column but forgot how to do that in R, so I did it in excel

maskd <- read_csv("C:/Users/Colin/Downloads/mask.csv")


m<-ggplot(maskd, aes(x = date, y = cases, group = condition, color = condition)) + geom_line(linewidth = 2) + scale_color_nejm() + theme(panel.background = element_rect(fill = "white", colour = "grey50"), legend.key = element_rect(fill = "white", color = NA)) + ggtitle("Kansas COVID-19 7-Day Rolling Average of Daily Cases/Per 100K Population") + theme(strip.background = element_rect(fill="white"), strip.text = element_text(size = 10, face = "bold")) + labs(subtitle = "Mask Counties Vs. No-Mask Mandate Counties", x = "Date", y = "Cases", color = "County Mask Requirement")

#the x axis looks crowded but once you open the graph in a separate window it actually looks okay. 

m


#I hate to do this every time, but it is really tempting to make this graph interactive
ggplotly(m)

```


The biggest problem with the old graph is that y axis on the left and y axis on the right side represent different values. My graph solved this problem, it is consistent and clear. Also, my graph shows the starting point or baseline for no mask vs. masked counties are very different. Mask mandate counties have higher daily cases to begin with than no mask counties.
What this tells us is wearing masks worked for counties with high covid cases because there's a huge drop in covid cases in the beginning and the end of the red line. We cannot really evaluate the effects of masks on no mask counties because they don't need to wear masks anyway. 
